Learning to Synthesize Rules for Rule-based Intrusion Detectors

### 2020-03-05 paper/paper.tex
minor changes

\vspace{-1ex}
\begin{table}[h!]
  \footnotesize
  \caption{\label{table:rules}Example of non-documentation options of Suricata.}
  \vspace{-2ex}
  \centering
  \begin{tabular}{clp{5.5cm}}
    \toprule
    \multicolumn{1}{c}{\#} & \multicolumn{1}{c}{Name} &  \multicolumn{1}{c}{Description}\\
    \midrule     
    1 & dsize & matches on the size of the packet payload\\
    2 & itype &  matches on a specific ICMP type\\
    3 & icode & matches on a specific ICMP code\\
    4 & icmp\_seq  & checks a ICMP sequence number\\
    5 & icmp\_id & matches on specific ICMP id-values\\
    6 & window & checks the size of the TCP window\\
    7 & flags & matches on TCP flags\\
    8 & fragbits & checks if the fragmentation or reserved bits are set in the IP header\\
    9 & threshold & minimum threshold for a rule before it generates alerts\\
    10 & content & checks if argument is present on the payload\\
    \bottomrule
  \end{tabular}
\end{table}
%\vspace{-1ex}

@@

\begin{figure}[t!]
\centering
\includegraphics[scale=0.28]{figs/ICMP-packet-structure.png}
\vspace{-2ex}
\caption{Layout of an ICMP packet.}
\label{fig:icmp-packet-layout}
\end{figure}
%\vspace{-2ex}

>>>>

\vspace{-1ex}
\begin{table}[h!]
  \footnotesize
  \caption{\label{table:rules}Example of non-documentation options of Suricata.}
  \vspace{-2ex}
  \centering
  \begin{tabular}{clp{6cm}}
    \toprule
    \multicolumn{1}{c}{\#} & \multicolumn{1}{c}{Name} &  \multicolumn{1}{c}{Description}\\
    \midrule     
    1 & dsize & matches on the size of the packet payload\\
    2 & itype &  matches on a specific ICMP type\\
    3 & icode & matches on a specific ICMP code\\
    4 & icmp\_seq  & checks a ICMP sequence number\\
    5 & icmp\_id & matches on specific ICMP id-values\\
    6 & window & checks the size of the TCP window\\
    7 & flags & matches on TCP flags\\
    8 & fragbits & checks if the frag. or reserved bits are set in the IP header\\
    9 & threshold & minimum threshold for a rule before it generates alerts\\
    10 & content & checks if argument is present on the payload\\
    \bottomrule
  \end{tabular}
\end{table}
%\vspace{-1ex}

@@

\begin{figure}[t!]
\centering
\includegraphics[scale=0.27]{figs/ICMP-packet-structure.png}
\vspace{-2ex}
\caption{Layout of an ICMP packet.}
\vspace{-2ex}
\label{fig:icmp-packet-layout}
\end{figure}
%\vspace{-2ex}
